### 2021-06-14 README.Rmd
add alt text to README figures

```{r diagram, echo=FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
```

@@

```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/README_files/figure-gfm/viz-1.png")
```

>>>>

```{r diagram, echo = FALSE, fig.cap = " ", fig.alt = "A diagram showing four steps to carry out randomization-based inference: specify hypothesis, generate data, calculate statistic, and visualize. From left to right, each step is connected by an arrow, while the diagram indicates that generating data and calculating statistics can happen iteratively."}
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
```

@@

```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE, fig.cap = " ", fig.alt = "A histogram showing a distribution of F statistics, right-tailed and centered around one half. The x axis ranges from zero to five. The region of the histogram to the right of the observed statistic, just above two, is shaded red to represent the p-value."}
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/README_files/figure-gfm/viz-1.png")
```
